All Your Graphs Belong to Us

### 2012-07-13 doc/asplos13/grappa.tex
Trival change to test repository move

\section{Grappa} \label{sec:grappa}

In this section we describe the Grappa runtime system (Figure~\ref{fig:grappa}).  Grappa is a software runtime system that one adds to a commodity HPC cluster.  It provides the following software abstractions to applications: \textbf{memory}, a global distributed shared memory and \textbf{tasking}, co-operative multithreading with automatic load balancing.  Under the hood a third component, \textbf{communication}, a network packet scheduler/aggregator is key to achieving high performance, but largely invisible to applications.  We will now describe each of these components.

@@

>>>>

\section{Grappa} \label{sec:grappa}
[trivial change]
In this section we describe the Grappa runtime system (Figure~\ref{fig:grappa}).  Grappa is a software runtime system that one adds to a commodity HPC cluster.  It provides the following software abstractions to applications: \textbf{memory}, a global distributed shared memory and \textbf{tasking}, co-operative multithreading with automatic load balancing.  Under the hood a third component, \textbf{communication}, a network packet scheduler/aggregator is key to achieving high performance, but largely invisible to applications.  We will now describe each of these components.

@@

Grappa provides its own task library to applications.  Applications begin execution with a single task, bound to an existing thread stack.  Tasks can spawn new tasks, and those new tasks are initially not bound to a thread stack, but instead are queued for future execution.

Grappa context switches between tasks non-preemptively.  Most calls into the Grappa library, however, do initiate a context switch, and tasks can explicitly yield control.  Grappa switches between tasks entirely within usermode, and in our experiments we have measured the context switch time to be only \checkme{40ns}.  This time is kept small because it is done entirely in usermode and only registers specified as caller saved by the compiler need be saved/restored.  Tasks become bound to a thread stack when no other task is runnable, or Grappa determines it is profitable to do so.  \TODO{How does Grappa determine this?}.

Tasks that are not bound to a stack are steelable by the work steeling system within Grappa.  This load balances work across the collection of nodes executing an application built on Grappa.  \TODO{Talk about the work steeling algorithm that we use}.
